\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-08 Thesis.tex
second submission

When writing a document or course notes in \stex, the creator general writes a top-level file such as \textit{notes.tex} from where other tex-files are included. These included files again include further tex-files etc.. Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths.\\

@@

\subsection{Relational Information}
\label{sec:relInfo}
\ednote{needs work}

@@

The order of information in certain topics will be referred to as levels. If we look at the pythagorean theorem and then realize we lack knowledge the concept of squares we could then read about that topic by going to that resource. From there on we are on a different \textit{level} which we can follow and dig deeper into until we understand squares.\\
\ednote{draw the whole graph and add here}
\ednote{add somewhere: By adding more levels of context we can allow viewers to understand the subject on a deeper level.}

@@

\subsection{Ordered Information Graphs}
\label{sec:orderedInfoGraphs}

@@

%narrative and mroe info

>>>>

When writing a document or course notes in \stex, the creator general writes a top-level file such as \textit{notes.tex} from where other tex-files are included. These included files again include further tex-files etc.. Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths. In essence, on any level the order of information in that topic is a narrative path.\\

@@

\subsection{Ordered Information Graphs}
\label{sec:orderedInfoGraphs}
\ednote{needs work}

@@

If we were to learn about the pythagorean theorem and then suddenly realized that we lack knowledge the concept of squares we could then learn about that topic by going to that resource. In other words, we check the dependencies of the pythagorean theorem, go that that level and follow the narrative path about squares until we understand squares. By adding a way to explore these other levels, the presentation adds more context and allows viewers to understand the subject on a deeper level.

\ednote{draw the whole graph and add here}

@@

\ednote{add example in slides and explain the different layers again}

@@
